---
title: "Investments Project"
author: "Yohari Hernandez"
date: "`r Sys.Date()`"
output:
  word_document: default
  html_document: default
---

# Senior Project

## Libraries required

```{r}
install.packages("quantmod")
install.packages("stats")
library(quantmod)
library(TSA)
library(tseries)

```

## Chapter 1 - Future value example

Creating the Future value function

```{r }
fv <- function(pmt, year,freq, yield, ordinary) {
  if(ordinary == 1) {
    i <- yield / freq
    n <- year*freq
    future <- pmt * ((1+i)^n - 1)/ i}
else
    future <- pmt * ((1+i)^n)-1 / (i / (1+i))
  return(future)

}

```

```{r}
fv(1440.82,30,12,.04,1) #calculating future value


rates <-seq(.01,.1, by=.01)

future_value <- fv(500,5,12,rates,1)
plot(rates, future_value, main = "Future Value vs Rates")
```

###################################### 

### Present Value

```{r}
#Present Value

pv <-function(payment, yield, span, freq, ordinary) {
  i<- yield/freq
  n<- span*freq
if(ordinary == 1){
  presentvalue <- payment * (1-(1+i)^-n)/i}
else
  presentvalue <- payment * (1-(1+i)^-n)/(i/(1+i))
return(presentvalue)
}

pv(500,.05,5,12,1)

yield <-seq(.01,.1, by=.01)

present_value <- pv(500, yield, 5,12,1) # the higher the yield the less we need present value will be.
plot(rates, present_value,main = "Present Value vs Yield")


```

########################### 

### Bonds

```{r}
Bondprice <- function(yield, couponrate, maturity, principal, freq) {
  i <- yield/freq
  r <- couponrate/freq
  n <- maturity*freq
  factor <- (1-(1+i)^(-n))/i
  couponamount<-(principal* r)
  price<- couponamount * factor + principal * ((1+i)^(-n))
return(price)
  
}
```

```{r}
Bondprice(.08,.06, 5, 1000,2)

yield <-seq(.01,.1, by=.01)

bond_price<- Bondprice(yield,.06,5,1000,2)
plot(yield, bond_price, main = "Bond Price vs Yield")
abline(v =.06, h=1000, col="red")

#when the yield price is equal to .06 the bond price is exactly to 1000, otherwise it will decrease as 
```

############## 

### Loan Amortization

```{r}
# calculate the balance of a loan
balance <- c()
interest.due <- c()
principal.repaid <- c()
result <- list()

#Loan balance function
loan.balance<- function(principal,rate, span, freq) {
  j <- rate/freq
  n <- span * freq
  v <- 1/(1+j)
  balance[1]<- principal
  pmt <- balance[1] * (j/(1-v^n)) 
  
for(i in 2:n) {
  interest.due[i]<- balance[i-1] * j #interest.due[1] is the interest incurred in period i
  principal.repaid[i]<- (pmt-interest.due[i]) #principal.repaid[i] the portion of pmt used to repay the ith balance.
  balance[i] <- balance[i-1]-principal.repaid[i]
}
  result<- list("Principal"=c(principal),"Payment"=c(round(pmt,2)),"Interest due"=c(round(interest.due,2)),"Principal   Repaid" =c(round(principal.repaid,2)),round(balance,2))
  print(result)
}

```

```{r}
loan.balance(20000,.05,5,12)
```

```{r}
Bondprice <- function(yield, couponrate, maturity, principal, freq) {
  i <- yield/freq
  r <- couponrate/freq
  n <- maturity*freq
  factor <- (1-(1+i)^(-n))/i
  # couponamount<-(principal* r)
  price<- principal* r * factor + principal * ((1+i)^(-n))
return(price)
  
}
```

```{r}

Bondprice(.06,.05,10,10000,2)
```

### Bondyield

```{r}
bondyield <- function(price, couponrate, maturity, principal, freq) #principal = facevalue
{
  
  pricediff <- function(x) {Bondprice(x,couponrate, maturity,principal, #x is always equal to yield
                                      freq) - price}
  irr <- uniroot(pricediff, c(-0.25, 20), tol=1e-08)
  return(irr$root)
}
```

```{r}
bondyield(9000,.05,10,10000,2)
```

####################################################### 

## A. Time series; noise; Random Walk; Geometric Random Walk

### A1. Weakly Stationarity:

A fundamental assumption for ARMA(Auto-regressive/Moving average) modelling is **the Weakly stationarity**

DEF: Time series{Y(t),t=1,2,...} is **weakly stationary If:**

(1) $E[Y(t)]= \mu$
(2) $Var[Y(t)] = \sigma^2$
(3) $cov(Y_t, Y_s) = \gamma(|t-s|), any \ s,t$
(4) $cor(Y_s, Y_t) = \rho(|t-s|), any \ s,t$

```{r}
library(TSA)
library(tseries)
data(larain)#Retrieving larain data
str(larain) #Reviewing time-series
time(larain) #Reviewing time series data from 1878 to 1992

plot(larain)
```

```{r}
data(beersales) #Retrieving beersales data
start(beersales)#start date of the time series = 1975
end(beersales) #end date of the time series = 1990
```

```{r}
plot(beersales, type ="l", main = "Beer sales from January 1975 to December 1990")
```

```{r}
data(airmiles) # pulling airmiles timeseries
start(airmiles)#start date of the time series = 1996
end(airmiles) #end date of the time series = 2005
frequency(airmiles) #freq is 12 # number of samples per unit time and deltat the time interval between observations

```

**Note:** **(i)** Can check Weakly Stationary by observing graph.

(1) Constant mean: Graph would be fluctuate vertically about a horizontal line.
(2) Constant variance: Graph would be "within" a band about that horizontal line.
(3) Constant for any equal "lag": $Y_s, Y_t$ have same "pattern" (both increase or both decrease)

**(ii)** Weakly Stationary can be checked by Dickey-Fuller test. `adf.test()` **Alternate hypothesis: Stationary**

```{r}
adf.test(larain) #the series is borderline stationary
paste("Since p-value > .05 we reject the null (borderline)")
```

```{r}

adf.test(beersales)#the series is stationary
paste("We have enough evidence that the time series larain is not a random walk, since p-value < .05 we fail reject the null")
```

```{r}
adf.test(airmiles)#the series is stationary
paste("We have enough evidence that the time series larain is not a random walk, since p-value < .05 we fail reject the null")
```

The first was border line but the 2nd and 3rd were not.

(iii) Most financial time series fail to be weakly stationary. So other models would be explored.

### **A2. NOISE:** Z(t) is called **Noise** if regression model residuals is N(0,sigma\^2):

(1) E[Z(t)]=0
(2) Var[Z(t)]=$\sigma^2$
(3) cov(Z(s),Z(t))=0 [uncorrelated] (totally random)

Z(t) Is a Gaussian Noise If Z(t)\~iid N(0,$\sigma^2$)

```{r}
x <- c(0,rnorm(99,0,2))
plot(x, type="l", main="Gaussian noise, N(0,2)")
```

NOTES; Noise iff (i) Mean 0: Graph would be about 0 (ii) Variance is constant, (iii) Randomly distributed about 0

Noises are weakly stationary

## **A3. RANDOM WALK:**

Let Y(t)=$\sum^tZ(t)$, where Z(t) Is a noise than Y is a Random Walk (a RW Is the cumulative sum of a Noise.)

In general, Y(t) Is a Random Walk iff, (1) E[Y(t)]=0 (2) Var[Y(t)] = t$\sigma^2$ (3) Cov(Y(t), Y(s))=0 (4) Cor(Y(t), Y(s))=0

```{r}
y <- c(0,cumsum(x))
plot(y, type = "l", main = "Random Walk")
abline(h=0, col="red")
```

Unless y(0)is specified, otherwise it will be randomly chosen.

**NOTES: For a Random Walk** (i) **Mean** in the long run would be 0: The graph is fluctuating about 0. (ii) **Non-constant variance:** The graph gets "wider" as t progresses However, graph would eventually return to 0 (by(i)) (iii) Zero autocorrelation.

## A4. Wiener process(or Brownin Motion)

NOTE: Any process W(t) can be written as: $W(t) = W(0) + \sum_{i=1}^{i=t} \bigtriangleup W(i), where \bigtriangleup W(i)=W(i)-W(i-1)$

$\bigtriangleup W(i)$ is called Increment or change at i

Any process can be written as "initial value" + "sum of the changes"

**A Weiner Process** (or Brownian Motion) W(i), if the:

Increments: $\bigtriangleup W(t) = W(t+ \bigtriangleup t) - W(t)$ satisfy

$\bigtriangleup W(t) = \in \sqrt{\bigtriangleup t} \ where \in \sim N(0,1), or \bigtriangleup W(i) \sim N(0,\sqrt{\bigtriangleup t})$

Ie, the increments are Normal distributed.

## NOTES

**(i)** $\bigtriangleup W(t) \sim N(0, \sqrt{\bigtriangleup t}). Or \bigtriangleup W(t) \sim N(0,\bigtriangleup t).. for Variance$

We say the increments are distributed as a Normal Noise.

**(ii)** For a Wiener process W(t) $W(t)=W(0)+ \sum_{i=1}^{i=t} \bigtriangleup W(i)$ W(t) becomes a Random Walk. (Review A3 Random Walk)

(i) E[w(t)]= w(0)
(ii) Var[w(t)] = t($\bigtriangleup t$)
(iii) Cov(w(t),w(s))=0

**(ii) If time is discretized into n increments:** {$t_0, t_1, t_2,..., t_{n-1},t_n = t \cdot \bigtriangleup t= \frac{t}{n}$}

$W(t) \sim N(W(0),t\sqrt{\bigtriangleup t}. Var(w_t - w_0) = n(\bigtriangleup t) = n(\frac{t}{n}) = t$

(a) The mean is W(0).
(b) Variance of a Weiner process Increases linearly with the length of time. The graph is wider and wider as t progress. (Similar with Random Walk graph)

**EXAMPLE: a Wiener process discretized with n=252 days**

```{r}
set.seed(100)
n <-252  #stock price days in the year
epsilon <- rnorm(n) #epsilon noise N(0,1)
mu <- 5
sigma <- 2
deltat <- 1/252
```

```{r}
plot(epsilon, type = "l", main =  "Normal Noise N(0,1)") #add into report
```

## Wienner

```{r}
w1 <- cumsum(epsilon*sqrt(1/n)) # The random walk
w1[1] #first element is 0.04773864
w1<-c(0,w1)
plot(w1, type = "l", main= "Wiener Processes")

w2<- cumsum(rnorm(n)*sqrt(1/n))
w2<-c(0,w2)

lines(w2, col="blue")


w3 <- cumsum(rnorm(n)*sqrt(1/n))
lines(w3, col="green")

abline(h=0, lty="dashed")
```

## Wiener Process with Drift

##Problem of Wiener Process with Drift

```{r}

Wiener1 <- (mu * deltat)  + (sigma * w1)


mu2 <- 10
sigma2 <- 2
deltat2 <- 1/252

Wiener2 <- (mu2 * deltat2)  + (sigma2 * w2)

plot(Wiener1, type ="l", main = "Wiener Process with Drift")
abline(h=0, lty="dashed")
lines(Wiener2, col="green")
legend("bottomleft", c("black : mu = 5, green: mu = 10"))

```

## Implementation

```{r}
library(quantmod)
```

```{r}
TSLA <- getSymbols("TSLA", from=start, to=end, auto.assign=F)

dim(TSLA) #757 and 6

head(TSLA)
```

```{r}
library(quantmod)
library(TSA)
library(tseries)


start<- as.Date("2019-12-31")
end <- as.Date("2022-12-31")

TSLA <- getSymbols("TSLA", from=start, to=end, auto.assign=F)

TSLA.Close <- TSLA$TSLA.Close
dim(TSLA) #757 and 6

head(TSLA)

class(TSLA) #XTs 

plot(TSLA$TSLA.Close, type="l")


```

```{r}
TSLA <- getSymbols("TSLA", from=start, to=end, auto.assign=F)

TSLA.Close <- TSLA$TSLA.Close
TSLA.return <- dailyReturn(TSLA$TSLA.Close)

plot( TSLA.return, type ="l")

```

```{r}

TSLA <- getSymbols("TSLA", from=start, to=end, auto.assign=F)

TSLA.Close <- TSLA$TSLA.Close
TSLA.return <- dailyReturn(TSLA$TSLA.Close)
TSLA.logret <- log(1+ TSLA.return)

plot( TSLA.logret, type ="l")
```

```{r}
rbar<- mean(TSLA.logret)
s<- sd(TSLA.logret)
N<-length(TSLA.logret)# 757
sigma.sqr <- s^2*N  # 1.562927
mu <- rbar*N   + sigma.sqr/2  # 2.26689
sigma<- sqrt(sigma.sqr) # 1.250171
cat("mu and sigma for the span", c(mu, sigma))

```

```{r}
TSLA.return
```

## Calculate the Cumulative Product (or Cumulative Return) of returns \Pi (1+R\left(i\right))

```{r}

# TSLA.CP <- cumprod(1+ TSLA.return)

prod(1+TSLA.return) - 1 # the formula

library(PerformanceAnalytics)

Return.cumulative(TSLA.return) # the shortcut

```

#####################################################################################33

```{r}
mean(TSLA.return)

summary(TSLA.return)

hist(TSLA.return)

qqnorm(TSLA.return) #checking normality
qqline(TSLA.return)

Box.test(TSLA.return)

install.packages(boot)
library(moments)
skewness(TSLA.return) #no skewness

kurtosis(TSLA.return) # above 3

TSLA.logret<- log(1+TSLA.return)
plot(TSLA.logret)

```

## This will be the analysis of Chevron

```{r}
start<- as.Date("2019-12-31")
end <- as.Date("2022-12-31")

CVX <- getSymbols("CVX", from=start, to=end, auto.assign=F) #Loading Chevron stock

CVX.Close <- CVX$CVX.Close


CVX.return <- dailyReturn(CVX$CVX.Close)

plot(CVX.Close, type ="l")
```

#Loading SHELL INC information

```{r}
getSymbols("SHEL", from = "2020-12-31", to="2021-12-31", auto.assign = F)
 
```

```{r}
SHEL <- getSymbols("SHEL", from="2020-12-31", to = "2022-12-31", auto.assign = F)
class(SHEL)
SHEL.Close <-  SHEL$SHEL.Close
plot(SHEL$SHEL.Close)
SHEL.return <- dailyReturn(SHEL$SHEL.Close)
plot(SHEL.return)
SHEL.yearly.return <- mean(SHEL.return) * 250
SHEL.yearly.return
```

## index(), Cl(); Ad(); as.Date(); subset of an xts-object

```{r}
date<- as.Date(index(TSLA.Close), format="%Y-%m-%d")

data1<- subset(TSLA.Close,  date >="2019-12-31" & date<= "2021-12-31")

```

A.  Beta of a stock

<!-- -->

1.  Read multiple stock prices

## Merging prices: merge()

```{r}
multi<- TSLA[  , 4]
multi <- merge(multi, TSLA[  ,4])
multi <- merge(multi, SHEL[  ,4])

class(multi)    # xts object
```

### Plot closing prices;NOTE: Its not a good plot

```{r}
plot(multi[  ,1], type="l", main=" Close Prices TSLA, SHEL, CVX")
lines(multi[  ,2], col="red")
lines(multi[  ,3], col="blue")
```

##### Many stocks ; Closing prices; (another way)

```{r}
prices<- NULL
TickerList <- c( "TSLA", "SHEL", "CVX")
for (Ticker in TickerList){
  prices <-cbind(prices, getSymbols.yahoo(Ticker, from=start, to=end, 
                                    verbose=F, auto.assign=F) [  ,4])} 


class(prices)    # xts,  index column shows up
```

1.  Calculate Returns (either use dailyReturn() package quantmod, or ROC(), package TTR)

```{r}
returns<- ROC(prices)   #xts object;in one step; 1st row has NA's
returns<- na.omit(returns)
```

2.  ChartsPerformanceSummary (package PerformanceAnalytics)

library(quantmod)

### Convert xts object to dataframe to use charts.PerformanceSummary()

```{r}
TSLA.Ret.df<- data.frame(TSLA.return)

charts.PerformanceSummary(TSLA.Ret.df, main="TSLA performance")

```

```{r}
TSLA.mu <- mean(TSLA.return)
TSLA.mu
```

```{r}
TSLA.mu.annual<- 252*AAPL.mu # 252 days?
TSLA.mu.annual

```

```{r}
TSLA.sigma <- sd(TSLA.return)
TSLA.sigma.annual<- sqrt(252)*TSLA.sigma
TSLA.sigma.annual


#NOTE:   expected return is 25.80%;  risk is 72.1%-  High expected return and high risk

```

3.  Correlation between stocks

NOTE:

```{r}
cor(returns)
```

REMARK: SHEL ,CVX returns are in HIGH correlation, since they are in the same industry(OIL&GAS). So the portfolio risk (variance/standard deviation) would be HIGH.

Sometimes, need to choose stocks from different industries to reduce the correlation is LOW, the portfolio risk is also LOW.

```{r}
chart.Correlation(returns)

```

4.  Benchmark Portfolio: is used to calculate the beta coefficient of a stock

SP500, Dow Jones; Nikei; Hangshen market index.

```{r}
djia <-getSymbols("^DJI", from=start, to=end, auto.assign=F)
nikei <-getSymbols("^N225",from=start, to=end, auto.assign=F)
hangshen <-getSymbols("^HSI",from=start, to=end, auto.assign=F)
```

```{r}
plot(djia[   ,4], type="l", col="red")
lines(nikei[  ,4], col="blue", lwd=2)
lines(hangshen[  ,4], col="green", lwd=2)
```

REMARK: All Market portfolio behave almost the same (high correlation) \# SP500 GSPC in Yahoo Finance (bench portfolio, S&P 500)

```{r}
bench <- getSymbols("^GSPC", auto.assign=F, src="yahoo",  from=start, to=end)[ ,4]

```

5.  Risk-free rate: is used to calculate the beta coefficient of a stock

############################################# 

###### Risk free rate ; Benchmark (SP500)

############################################# 

```{r}
## risk-free rate(changing wrt time)
rf<-getSymbols("TB3MS",src="FRED" ,auto.assign = F)

rf<-getSymbols("TB3MS",src="FRED" ,auto.assign = F)
head(rf)
```

```{r}
rf<-getSymbols("TB3MS",src="FRED" ,auto.assign = F) # TB3MS 3-Month Treasury Bill Secondary Market Rate, Discount Basis 
date<- as.Date(index(rf))
# rf1 <- rf[ date >= "2019-12-31"  & date<="2022-12-31",  ]

rfr <- window(rf,start = start, end=end)
```

```{r}
head(rf1)
```

```{r}
rf1<- rf1/100
head(rf1)
```

6.  Market portfolio index( benchmark portfolio); SP500

```{r}
bench<-getSymbols.yahoo("^GSPC", from=start, to=end, periodicity = "daily",auto.assign=F)[  ,4]

bench.returns <- dailyReturn(bench)  

```

7.  Compare stocks performance with bench mark portfolio

################################################ 

######## Plot TSLA, SHEL, CVX and bench portfolio (market portfolio)

################################################ 

```{r}

bench.CP <- cumprod(1+bench.returns)

SHEL.CP<- cumprod(1+ SHEL.return)
TSLA.CP <- cumprod(1+ TSLA.return)
CVX.CP <- cumprod(1+ CVX.return)

plot(bench.CP, type="l", ylim=c(0, 3))
lines(TSLA.CP, type="l", col="blue")

lines(CVX.CP, type="l", col="red")

lines(SHEL.CP, type="l", col="green")

```

8.  Calculate beta coefficients of a stock

#### beta's using regression model, assume riskfree rate is changing

```{r}
TSLA.excess <- TSLA.return -rf1
bench.excess <- bench.returns -rf1
TSLA.beta<- coefficients(lm(TSLA.excess ~ bench.excess ))[2]
TSLA.beta
```

```{r}
CVX.excess <- CVX.return -rf1
bench.excess <- bench.returns -rf1
CVX.beta<- coefficients(lm(CVX.excess ~ bench.excess ))[2]
CVX.beta
```

9.  CAPM Beta (Capital Asset Price Model): We have another Beta called CAPM Beta,

Which calculation also involves the Stock Excess Return , Market Excess Return.

$$CAPM.?? =  cov(R-rf,R_M-rf)/var(R_M )$$

```{r}
CAPM.beta<- cov(TSLA.return, bench.returns)/var(bench.returns)
CAPM.beta

```

### DIRECTIONS: Choose 5 stocks, from different industries( IT, automobiles, retails, drugs) , over a time span of 2 years .

### Review Supplement#3

        Choose the optimal portfolio , using highest Sharp coefficient: 

```{r}
library(quantmod)
library(TSA)
library(tseries)

start<- as.Date("2020-12-31")
end <- as.Date("2022-12-31")

TSLA <- getSymbols("TSLA", from=start, to=end, auto.assign=F)#loading Tesla
TSLA.Close <- TSLA$TSLA.Close
TSLA.return <- dailyReturn(TSLA$TSLA.Close)
TSLA.logret <- log(1+ TSLA.return)

CVX <- getSymbols("CVX", from=start, to=end, auto.assign=F)#loading Chevron
CVX.Close <- CVX$CVX.Close
CVX.return <- dailyReturn(CVX$CVX.Close)
CVX.logret <- log(1+ CVX.return)

COST <- getSymbols("COST", from=start, to=end, auto.assign=F) #loading Costco
COST.Close <- COST$COST.Close
COST.return <- dailyReturn(COST$COST.Close)
COST.logret <- log(1+ COST.return)

PEP <- getSymbols("PEP", from=start, to=end, auto.assign=F) #loading Pepsi
PEP.Close <- PEP$PEP.Close
PEP.return <- dailyReturn(PEP$PEP.Close)
PEP.logret <- log(1+ PEP.return)

AMC <- getSymbols("AMC", from=start, to=end, auto.assign=F) #loading AMC Theathers
AMC.Close <- AMC$AMC.Close
AMC.return <- dailyReturn(AMC$AMC.Close)
AMC.logret <- log(1+ AMC.return)

```

1.  Beta \> 1.5 or 2

```{r}
bench<-getSymbols.yahoo("^GSPC", from=start, to=end, periodicity = "daily",auto.assign=F)[ ,4]
bench.returns <- dailyReturn(bench)
```

```{r}
#find beta of Costco
bench.excess <- bench.returns -rf1
COST.excess <- COST.return - rf1
COST.beta<- coefficients(lm(COST.excess ~ bench.excess ))[2]

COST.beta # .4202


#find beta of Tesla
TSLA.excess <- TSLA.return - rf1
TSLA.beta<- coefficients(lm(TSLA.excess ~ bench.excess ))[2]

TSLA.beta # 1.8561

#find beta of Chevron
CVX.excess <- CVX.return - rf1
CVX.beta<- coefficients(lm(CVX.excess ~ bench.excess ))[2]

CVX.beta # .2882

#find beta of Pepsico
PEP.excess <- PEP.return - rf1
PEP.beta<- coefficients(lm(PEP.excess ~ bench.excess ))[2]

PEP.beta # .3397

#find beta of AMC Theathers
AMC.excess <- AMC.return - rf1
AMC.beta<- coefficients(lm(AMC.excess ~ bench.excess ))[2]

AMC.beta # 3.4235

```

2.  PE \> 20

```{r}
 wts1 <- c(.20,.20,.20,.20,.20)
```

3.  Investigate the Annualized Expected returns/Annualized Risk for each stock.

## Portfolio expected return

```{r}
# cbind() all returns of those stocks into one xts-object, named "returns"
returns <- cbind(TSLA.return,COST.return,CVX.return,PEP.return, AMC.return)
colnames(returns)<- c("TSLA.return","COST.return","CVX.return","PEP.return", "AMC.return")
head(returns)
```

#calculate the expected return (average) of all those stocks

```{r}
return.means<- apply(returns,2,mean)
return.means



```

```{r}
port.ret1 <-252* t(wts) %*% return.means
port.ret1

## Calculate the Portfolio variance/risk
cov <- cov(returns)
cov.annual <- 252*cov
port.var <- t(wts1) %*% cov.annual %*% wts1
port.var
```

```{r}
port.sd <- sqrt(port.var)
port.sd 
```

4.  Correlation

```{r}
library(PerformanceAnalytics)
chart.Correlation(returns)
```

################################################################################################################################################################################################################################################################################################################################################################################# 

5.  Perform portfolio analysis as in part B. Plot the Efficient Frontier.

```{r}
# Create weights, sum is 1.0, from -2.0 to 2.0 : A For-loop

wts<-c(0,0,0,0,0)

for (i in 1:100){
   wt <- c(0,0,0,0,0)
  wt[1]<- runif(1, -2,2)
  wt[2]<- runif(1, -2,2)
  wt[3]<- runif(1, -2,2)
  wt[4]<- runif(1, -2,2)
  wt[5]<- 1-wt[1] -wt[2] -wt[3] -wt[4]
 
 
  wts<- cbind(wts,wt )
}

head(wts)
# wts<-c(0,0,0,0,0)
# for (i in 1:100){
# wt<- c(runif(1, -2,2),runif(1, -5,5), 1 -wt[1]-wt[2]-wt[3]-wt[4]-wt[5])
# wts<- cbind(wts,wt )
# }
```

```{r}
return.means<- apply(returns,2,mean)
return.means
```

```{r}
cov<-cov(returns)

# port.variance <-c()
# for (i in 1:101) {
# port.variance[i] <- t(wts)[i, ] %*% cov %*% wts[ , i ]
# }
# head(port.variance)

```

```{r}
# port.ret <- c() 
# for (i in 1:101){ port.ret[i] <- t(wts)[i, ] %*% return.means } 
# head(port.ret)

```

```{r}
port.risk <-sqrt(port.variance)
head(port.risk)

```

```{r}


```

```{r}
plot(port.risk, port.return, type="b",
main="Efficient Frontier, AAPL+TSLA+FMST")
```

6.  Choose the highest Sharp coefficient:

```{r}

```
